\documentclass[9pt,addpoints]{exam}
\usepackage{enumitem}
\usepackage{amsfonts,amssymb,amsmath, amsthm}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{pgf,tikz,pgfplots}
\pgfplotsset{compat=1.15}
\usepgfplotslibrary{fillbetween}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\pagestyle{headandfoot}
%\firstpageheadrule
\runningheader{Homework 6}{}{Page \thepage\ of \numpages}
\runningheadrule
\author{Aaron GK}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=10mm,
	right=10mm,
	bottom=5mm,
	top=5mm,
}
\firstpagefooter{}{}{}
\runningfooter{}{}{}


\begin{document}
	\title{St John Baptist De La Salle Catholic School, Addis Ababa\\
		\large Homework 6 \\
		2nd Quarter}
	\maketitle
	\begin{center}
		\fbox{\fbox{\parbox{6in}{\centering
					Notes, and use of other aids is allowed.  Read all directions carefully and write your answers in the space provided.  To receive full credit, you must show all of your work. \textbf{Cheating or indications of cheating and similar answers will be punished accordingly}. 
		}}}
		\subsubsection*{Information}
		\begin{itemize}
			\item The homework is due on \textbf{Thursday}, \textbf{January 5th}.
			\item You should Work on it \textbf{individually} and consult me if you have any questions. As I have reiterated multiple times, cheating will have a serious consequence.
			\item For purposes of neatness and simplicity of grading, you should do the homework on an \textbf{A-4 paper}.
		\end{itemize}
	\end{center}
	\begin{center}
		\subsection*{Questions}
	\end{center}
	
	\begin{questions}
		\question A parallel-plate capacitor has a capacitance of 20$\mu$F. If the separation between the plates of the capacitor is 20mm, and the plates are squares of side length 3cm. If the plates store a charge of 20$\mu$C, what is the potential difference across the plates of the capacitor. Find the energy stored in the capacitor.
		\question What is a dielectric and what role does it play in capacitors? Why does the presence of dielectric materials increase the capacitance of capacitors?
		\question Calculate the work done by a 1.5V battery as it charges a 35nF capacitor in the flash unit of a camera.
		\question Teflon has a dielectric constant of 2.1. If Teflon was placed between the plates of the capacitor in question 1, find \begin{itemize}
			\item Teflon's permissivity
			\item The capacitance of the capacitor with teflon as a dielctric. 
		\end{itemize}
		\subsection*{Additional Challenge Problems}
		\textit{As usual, the following problems are not required to be submitted, but I highly suggest you work on them} 
		\question Show, mathematically that the capacitance of a parallel plate capacitor of area A and plate separation distance d has a capacitance of $\text{C}=\epsilon_0\dfrac{\text{A}}{\text{d}}$. In addition, show that when a dielectric with a constant of $\kappa$ is added between the plates, show that the capacitance changes to $\text{C}=\kappa\epsilon_0\dfrac{\text{A}}{\text{d}}$
		\question Consider a region in space where a uniform electric field of E = 1000 N/C points in the positive X direction. Answer the following questions:\begin{itemize}
			\item What is the orientation of the equipotential surfaces?
			\item If you move in the negative X direction, does electric potential decrease or increase?
			\item What is the distance between the +20 V and + 10 V potentials?
		\end{itemize}
	\end{questions}		
\end{document}