\documentclass[9pt,addpoints]{exam}
\usepackage{enumitem}
\usepackage{amsfonts,amssymb,amsmath, amsthm}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{pgf,tikz,pgfplots}
\pgfplotsset{compat=1.15}
\usepgfplotslibrary{fillbetween}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\pagestyle{headandfoot}
%\firstpageheadrule
\runningheader{Group Project}{}{Page \thepage\ of \numpages}
\runningheadrule
\author{Aaron GK}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=10mm,
	right=10mm,
	bottom=5mm,
	top=5mm,
}
\firstpagefooter{}{}{}
\runningfooter{}{}{}
\begin{document}
	\title{St John Baptist De La Salle Catholic School, Addis Ababa\\
		\large Group Project \\
		2nd Quarter}
	\maketitle
	\begin{center}
		\subsubsection*{Information}
		\begin{itemize}
			\item The group project is due is due on \textbf{Monday}, \textbf{January 9th}.
			\item You should work on the projects \textbf{in groups} and consult me if you have any questions. Every member should have meaningful contribution to the project.
			\item The assignment should be submitted via email(\textbf{aaron@stjohn.edu.et} or \textbf{aaron@sjbdcs.org}) as a PDF file. You can alternatively choose to submit a hard-copy paper submission.
		\end{itemize}
	\end{center}
	\begin{center}
		\subsection*{Requirements}
	\end{center}
	\subsubsection*{Original Content \& No direct plagiarism } 
	The paper you submit should be as original as possible and not a direct plagiarized content from others' work. To that end, the originality of your paper has a weight of \textbf{25}\%.
	\subsubsection*{Actuality \& Scientific Truth}
	The paper submitted should be based on a scientifically accepted truth/fact. This, again, has a weight of \textbf{25}\%.
	\subsubsection*{Written in Proper English}
	The paper submitted should be written in a language that is grammatically correct and should make sense. This has a weight of \textbf{20}\%
	\subsubsection*{Presentation \& Slides}
	The group project will be presented and should have PowerPoint /Beamer slides. The presentation along with the quality of the slides has a weight of \textbf{30}\% \\ \\
	\textbf{Extrapoints}\\
	As an incentive to push all of you into scientific endeavors, there will be extra points for doing the following:
	\begin{itemize}
		\item A paper written in LaTex.
		\item Slides made with Beamer.
		\item If you include relevant material in your presentation or provide in addition(for instance, could be codes for simulations)
	\end{itemize}
	The maximum extra points you will get will be 20\% of the total weight of the project.
\end{document}