\documentclass[12pt,addpoints]{exam}
%\usepackage{enumitem}
\usepackage{amsfonts,amssymb,amsmath, amsthm}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{pgf,tikz,pgfplots}
\pgfplotsset{compat=1.15}
\usepgfplotslibrary{fillbetween}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=15mm,
	right=15mm,
	bottom=20mm,
	top=15mm,
}
\date{June, 2023}
\pagestyle{headandfoot}
%\firstpageheadrule
\runningheader{4th Quarter Final Examination}{}{Page \thepage\ of \numpages}
\runningheadrule
\firstpagefooter{}{}{}
\runningfooter{By Aaron G.K.}{}{Page \thepage\ of \numpages}
\begin{document}
	\title{St John Baptist De La Salle Catholic School, Addis Ababa\\
		\large \textbf{Grade 10B} Physics Final Examination \\
		Summer Term}
	\maketitle
	{Name:\underline{\hspace{2in}}\text{\hspace{.3in}}{Section:\underline{\hspace{0.3in}}\hspace{.3in}{Time Allowed: \bf{25 minutes}}
				\subsubsection*{Multiple Choice Questions}
				\begin{questions}
					\question When light travels from glass into air, which of the following statements is accurate?
					\begin{choices}
						\choice The wavelength decreases, and the speed decreases.
						\choice The wavelength decreases, and the speed increases. 
						\choice The wavelength increases, and the speed decreases.
						\choice The wavelength increases, and the speed increases.
					\end{choices}
					\question The speed of light in a given medium is about $2.0\times10^8m/s$. What is the refractive index of this medium? \\
					\begin{oneparchoices}
						\choice 1
						\choice 2
						\choice 2.5
						\choice 1.5
					\end{oneparchoices} 
					\question How accurately (in nanoseconds) must you be able to measure the echo time to an airplane 12.0
					km away to determine its distance within 15.0 m? \\
					\begin{oneparchoices}
						\choice 50
						\choice 100
						\choice 80
						\choice 66.7
					\end{oneparchoices}
					\question Light is incident into air from a medium at an angle of $50^0$. If the refractive index of the the medium is 2, what happens to the light ray? \\
					\begin{oneparchoices}
						\choice Undergoes refraction
						\choice $50^0$ is the critical angle \\
						\choice Total internal reflection
						\choice None of the above
					\end{oneparchoices}
					\question Assume a person is swimming inside a pool of water. When watching an object outside the pool, does it look nearer or farther? \\
					\begin{oneparchoices}
						\choice It is the same distance
						\choice It looks nearer \\
						\choice It looks farther
						\choice None of the above
					\end{oneparchoices} 
					\subsection*{Workout Problems}
					\question Using the concepts of RBG vision and Raleigh scattering explain why we perceive of the sky as being blue?\vspace{1in}
					\question A 12cm tall object is placed 15 cm away from a 5 cm focal length convex lens.
					\begin{itemize}
						\item What is the distance between the image and the object?\vspace{1.5in}
						\item What is the magnification by the lens? What about the power?\vspace{1.5in}
						\item What is the height of the image?\vspace{1.5in}
						\item List and explain why whether the image is real/virtual and upright/inverted.\vspace{1.5in}
					\end{itemize}
				\end{questions}
				
			\end{document}