\documentclass[11pt,addpoints]{exam}
%\usepackage{enumitem}
\usepackage{amsfonts,amssymb,amsmath, amsthm}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{pgf,tikz,pgfplots}
\pgfplotsset{compat=1.15}
\usepgfplotslibrary{fillbetween}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=20mm,
	top=20mm,
}
\date{March, 2023}
\pagestyle{headandfoot}
%\firstpageheadrule
\runningheader{3rd Quarter Midterm Reexamination}{}{Page \thepage\ of \numpages}
\runningheadrule
\firstpagefooter{}{}{}
\runningfooter{By Aaron G.K.}{}{Page \thepage\ of \numpages}
\begin{document}
	\title{St John Baptist De La Salle Catholic School, Addis Ababa\\
		\large Grade 10 Physics Midterm Reexamination \\
		$3^\text{rd}$ Quarter}
	\maketitle
	\begin{center}
		\fbox{\fbox{\parbox{6in}{\centering
					Notes, and use of other aids is \textbf{NOT} allowed.  Read all directions carefully and \textbf{write your answers in the answer sheet}.  To receive full credit, you must show all of your work.
	}}}	\end{center}
	{Name:\underline{\hspace{2in}}\text{     }{Roll Number:\underline{\hspace{0.5in}}\text{     }{Section:\underline{\hspace{0.3in}}{Time Allowed: \bf{1 hour}}
				\subsubsection*{Multiple Choice Questions}
				\begin{questions}
					\question Which of the following is true about the difference between electric and magnetic fields?
					\begin{choices}
						\choice Magnetic fields are closed loops while electric fields don't necessarily need to be like that.
						\choice Magnetic fields can exist only from monopoles while electric fields need both parities to emerge.
						\choice Electric fields give rise to conservative fields while magnetic fields give rise to dissipative fields.
						\choice Electric fields and magnetic fields are the same.
					\end{choices}
					\question What is the SI unit of magnetic field strength? \\ \begin{oneparchoices}
						\choice Weber
						\choice Volt
						\choice Tesla
						\choice Coulomb
					\end{oneparchoices}
					\question A cosmic ray electron moves at $7.5\times10^{6}m/s$ perpendicular to the Earth’s magnetic field at an altitude where field strength is $1.00\times10^{-5}T$. What is the radius of the circular path the electron follows?\\ \begin{oneparchoices}
						\choice 4.27m
						\choice 3m
						\choice 2m
						\choice 3.2m
					\end{oneparchoices}
					\question A positive charge moving to the right with a constant velocity enters a region of a uniform magnetic field pointing into the page. What is the direction of the magnetic force on the charge?\\ \begin{oneparchoices}
						\choice Left
						\choice Right
						\choice To the top
						\choice To the bottom
						\choice N/A
				\end{oneparchoices}		
					\question A DC power line for a light-rail system carries 1000 A at an angle of $30^0$ to the Earth’s $5\times10^{-5}T$ field. What is the force on a 100-m section of this line?\\ \begin{oneparchoices}
						\choice 2.50 N
						\choice 3.2 N
						\choice 1 N
						\choice 2 N
					\end{oneparchoices}
					\question For a charge to experience a force due to a magnetic field, it has to: \\ \begin{oneparchoices} 
							\choice be moving
							\choice have a charge
							\choice move perpendicular to the field
							\choice All
					\end{oneparchoices}
					\question Who was the first person to have discovered that current carrying wires induce magnetic fields? \\ \begin{oneparchoices}
						\choice Oersted
						\choice Faraday
						\choice Henry
						\choice Curie
					\end{oneparchoices} 	 
					\question Why are magnets named magnets?
					\begin{choices}
						\choice Because they were discovered at a place called Magnesia
						\choice Because they were discovered by a person called Magnesia
						\choice Because they were discovered at an era called Magnesia
						\choice All
					\end{choices}
					\question What is the angle between a wire carrying an 8.00-A current and the 1.20-T field it is in if 50.0 cm of the wire experiences a magnetic force of 2.40 N? \\ \begin{oneparchoices}
						\choice $\dfrac{\pi}{3}$ 
						\choice $\dfrac{\pi}{6}$
						\choice $\dfrac{\pi}{2}$
						\choice $\dfrac{\pi}{4}$
					\end{oneparchoices}
					\question An AC appliance cord has its hot and neutral wires separated by 4.00 mm and carries a 6.00-A current. Which of the following is true?\begin{choices}
						\choice The force between the two wires is attractive.
						\choice The force between the two wires is repulsive.
						\choice Since the force is large, we need to design specific features to minimize the force.
						\choice Since the force is small, no specific design features are necessary.
					\end{choices}
				\subsubsection*{Workout Problems}
					\question How strong is the magnetic field inside a solenoid with 10,000 turns per meter that carries 20.0 A?\vspace{0.8in}
					\question An electron in a TV CRT moves with a speed of $8.00\times10^{7}m/s$, in a direction perpendicular to the Earth’s field, which has a strength of $5\times10^{-5}T$. 
					\begin{enumerate}
						\item What strength electric field must be applied perpendicular to the Earth’s field to make the electron moves in a straight line?\vspace{0.8in}
 						\item If this is done between plates separated by 4.00 cm, what is the voltage applied?\vspace{0.8in}
					\end{enumerate}
					\question Show that the units of $Nm$ and $Am^2T$ are the same.\vspace{0.7in}
					\question Show that the charge to mass ratio of a charge accelerated by a voltage V is $\dfrac{2V}{B^2R^2}$
					\end{questions}
			\end{document}