\documentclass[13pt,addpoints]{exam}
%\usepackage{enumitem}
\usepackage{amsfonts,amssymb,amsmath, amsthm}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{pgf,tikz,pgfplots}
\pgfplotsset{compat=1.15}
\usepgfplotslibrary{fillbetween}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=20mm,
	top=20mm,
}
\date{December, 2022}
\pagestyle{headandfoot}
%\firstpageheadrule
\runningheader{1st Quarter Midterm Prep}{}{Page \thepage\ of \numpages}
\runningheadrule

\firstpagefooter{}{}{}
\runningfooter{By Aaron G.K.}{}{Page \thepage\ of \numpages}


\begin{document}
	\title{St John Baptist De La Salle Catholic School, Addis Ababa\\
		\large Physics Midterm Prep \\
		$2^\text{nd}$ Quarter}
	\maketitle
	\begin{center}
		\fbox{\fbox{\parbox{6in}{\centering
					Notes, and use of other aids is \textbf{NOT} allowed.  Read all directions carefully and \textbf{write your answers in the answer sheet}.  To receive full credit, you must show all of your work.
		}}}
		\subsubsection*{Useful Constants}
		\begin{itemize}
			\item $\textbf{a}_g=10m/s^2\text{  - acceleration due to gravity}$\textbf{~}$\textbf{G} = 6.672\times10^{-12}\frac{Nm^2}{kg^2}\text{  - gravitational constant}$
		\end{itemize}
		
	\end{center}
				\begin{questions}
					\question If the net torque in a system is 0, what can we say about the angular velocity, angular momentum, the torques on the system? 
					\question What are the physics concent behind each of Kepler's Laws of Planetary Motion(try to prove each one)? 
					\question The trajectory of planets \& celestial bodies around the sun can only be a few shapes - what are they? 
					\question What are the factors affecting moment of inertia? How does the moment of inertia change if we change the factors?
					\question How was the gravitational constant discovered? 
					\question Why do we have the door handles away from the hinges?
					\question Prove Kepler's Third Law.(\textit{For the sake of simplicity, assume the path of planets is circular)}.
					\question If a planet is orbitting the sun 10 AU away, find its period.
					\question Convert the following quantities into their standard units:
					\begin{itemize}
						\item 2 rev/min
						\item 10 rev/s
						\item 900$^0$
						\item 100 revolution
						\item 7 rev/min$^2$
					\end{itemize}
				\end{questions}
			\end{document}