\documentclass[12pt,addpoints]{exam}
%\usepackage{enumitem}
\usepackage{amsfonts,amssymb,amsmath, amsthm}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{pgf,tikz,pgfplots}
\pgfplotsset{compat=1.15}
\usepgfplotslibrary{fillbetween}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=15mm,
	right=15mm,
	bottom=20mm,
	top=15mm,
}
\date{June, 2023}
\pagestyle{headandfoot}
%\firstpageheadrule
\runningheader{4th Quarter Final Examination}{}{Page \thepage\ of \numpages}
\runningheadrule
\firstpagefooter{}{}{}
\runningfooter{By Aaron G.K.}{}{Page \thepage\ of \numpages}
\begin{document}
	\title{St John Baptist De La Salle Catholic School, Addis Ababa\\
		\large \textbf{Grade 10A} Physics Final Examination \\
		Summer Term}
	\maketitle
	{Name:\underline{\hspace{2in}}\text{\hspace{.3in}}{Section:\underline{\hspace{0.3in}}\hspace{.3in}{Time Allowed: \bf{25 minutes}}
			\subsubsection*{Multiple Choice Questions}
			\begin{questions}
				\question A ball is thrown at an angle of 50 degrees above the horizontal. Which of the following best describes the acceleration of the ball from the instant after it leaves the thrower's hand until the time it hits the ground?
				\begin{choices}
					\choice Always in the same direction as the motion, initially positive and gradually dropping to zero by the time it hits the ground
					\choice Initially positive in the upward direction, then zero at maximum height, then negative from there until it hits the ground
					\choice Always in the opposite direction as the motion, initially positive and gradually dropping to zero by the time it hits the ground
					\choice Always in the downward direction with the same constant value
				\end{choices}
				\question What is the displacement of a ball thrown straight up with an initial velocity of $15.0m/s$? (Assume $g=9.8m/s^2$) \\
				\begin{oneparchoices}
					\choice 6.28m
					\choice 1.1m
					\choice 14m
					\choice 10.4m
				\end{oneparchoices}
			  \question A basketball referee tosses the ball straight up for the starting tip-off. At what velocity must a basketball player leave the
			  ground to rise 1.25 m above the floor in an attempt to get the ball? \\
			  \begin{oneparchoices}
			  	\choice 3.5 m/s
			  	\choice 2.2 m/s
			  	\choice 1.3 m/s 
			  	\choice 4.95 m/s
			  \end{oneparchoices}
		  		\question You throw a ball straight up with an initial velocity of 15.0 m/s. It passes a tree branch on the way up at a height of 7.00
		  		m. How much additional time will pass before the ball passes the tree branch on the way back down? \\
		  		\begin{oneparchoices}
		  			\choice 7 s
		  			\choice 4 s
		  			\choice 1.91 s
		  			\choice 9 s
		  		\end{oneparchoices}
	  			\question What is the velocity of a projectile at the maximum height? \\
	  			\begin{oneparchoices}
	  				\choice 0
	  				\choice $v_y$
	  				\choice $v_x$
	  				\choice $v_i$
	  			\end{oneparchoices}
				\subsection*{Workout Problems}
				\question Discuss what happens to the velocity(\textit{both horizontal and vertical}) of a projectile at maximum height\vspace{1in}
				\question A softball of mass 4 kg is thrown with an initial velocity of 10 m/s at an angle $\theta$ to the horizontal. When the ball reaches
				its maximum height, its kinetic energy is 50 J.
				\begin{itemize}
					\item At what angle was the ball thrown?\vspace{1.5in}
					\item What is the maximum height achieved by the ball from its point of release?? What about the power?\vspace{1.5in}
					\item How long after the ball is thrown will it return to the ground?\vspace{1.5in}
					\item Calculate the horizontal distance that the ball will travel during its flight.\vspace{1.5in}
				\end{itemize}
			\end{questions}
			
		\end{document}