\documentclass[11pt]{article}
%\voffset -.5in \hoffset -.5in \textheight 9.9in \textwidth 6.4in
\usepackage{geometry,url}
\geometry{body={7in,9.3in}, centering}
\pagestyle{empty}
\usepackage{multicol}
\begin{document}
	\begin{center}
		\textbf{\Large Special Topics in Physics}\\
		St John Baptist De La Salle Catholic School, Addis Ababa\\ Department of Physics\\ SP001
	\end{center}
	%\framebox[6.2in]{\makebox[\totalheight]}
	
	%\begin{tabular}{l@{\qquad}l@{\qquad}l@{\qquad}}
	%   Course Title: & &  \\
	%  \end{tabular}
------------------------------------------------------------------------------------------------------------------------------------
\vspace{-.1in}
\begin{center}
	\begin{tabular}{llll}
		\textbf{Instructor:} & \footnotesize{(Aaron GK)}  &   \textbf{Class Location:}  & \footnotesize{(Eamon De Valera Data Center \& Google Meet)}\\ 
		\textbf{Email:} & \footnotesize{(aaronkebede@stjohn.edu.et)} &   \textbf{Class Day/Time:} & \footnotesize{(Every day from 11am to 12pm)}\\
		\textbf{Office Hours:} & \footnotesize{(12-12:30pm everyday)} & \textbf{Office Location:} & \footnotesize{(Staff \& Google Meet)}\\
		\textbf{Course Language:} & \footnotesize{(English/Amharic)} & \textbf{Term:} &   \footnotesize{(Semester Break)} \\
	\end{tabular}
\end{center}

------------------------------------------------------------------------------------------------------------------------------------
%{Spring 2011}

\noindent {\bf COURSE DESCRIPTION}\\
Special topics in physics: cosmology \& high energy physics, general relativity \& quantum gravity, phenomenology.

\medskip\noindent {\bf STUDENT LEARNING OUTCOMES}\\
The successful student in this course should be able to:
\begin{itemize}
	\item Understand and simply explain the inspiration for research in fundamental physics topics.
	\item Have an adequate understanding of the history of Cosmology, current research topics \& important outlooks for the future.
	\item Have an adequate understanding of the history of Dark Matter, current research topics \& important outlooks for the future.
	\item Have an adequate understanding of the history of String theory, current research topics \& important outlooks for the future.
	\item Have an adequate understanding of the acquainting quantum physics \& general relativity, attempts to reconcile the subjects, current research topics \& important outlooks for the future.
\end{itemize}

\noindent {\bf PREREQUISITES}\\ 
Since this is an extremely introductory course, no prior knowledge is required, however, a physics background helps.\\

\noindent{\bf TEXTBOOK:}{\sl \  Openstax College Physics 2e}\\ \\
Good news: your textbook for this class is available for free online, in web view and PDF format!\\
You can use whichever formats you want. Web view is recommended -- the responsive design works seamlessly on any device.\\ \\
\textbf{www.openstax.org/details/books/college-physics-2e}\\

\noindent{\bf GRADING AND EVALUATION}\\ 
There will be a quiz everyday after class that should be attempted before the end of the next class. At the end of the course, you are expected to write a paper in the topic of your interest that aligns with the course.\\ \\
\end{document}