\documentclass[12pt,addpoints]{exam}
\usepackage{enumitem}
\usepackage{amsfonts,amssymb,amsmath, amsthm}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{pgf,tikz,pgfplots}
\pgfplotsset{compat=1.15}
\usepgfplotslibrary{fillbetween}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\pagestyle{headandfoot}
\firstpageheadrule
\runningheader{Grade 9 Biology Workbook Questions}{}{Page \thepage\ of \numpages}
\runningheadrule
\author{St John Baptist De La Salle Catholic School, Addis Ababa}
\firstpagefooter{}{}{}
\runningfooter{}{}{}
\date{22/23 Academic Year}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=15mm,
	right=15mm,
	bottom=20mm,
	top=15mm,
}

\begin{document}
	\title{Grade 9 Biology Workbook Questions}
	\maketitle
	\begin{center}
		\subsection*{Multiple Choice}
	\end{center}
	\begin{questions}
		\question A type of an unspecialized cell that is important for cell replacement and repair is \\
		\begin{oneparchoices}
			\choice hemotopoetic stem cell
			\choice embryonic stem cell
			\choice adult stem cell
			\choice None
		\end{oneparchoices}
		\question Particles can move across the cell membrane without needing a transport or a carrier protein if they are \\
		\begin{oneparchoices}
			\choice small
			\choice uncharged
			\choice lipid soluble
			\choice All
		\end{oneparchoices}
		\question All amino acids have a basic structure which consists of \\
		\begin{choices}
			\choice an amino group, a carboxyl group, and a side chain
			\choice phosphate and alcohol groups
			\choice amino group and alchohol
			\choice glycerol
		\end{choices}	
		\question Which type of lipid is formed from a glycerol, two fatty acids, and a phosphate group? \\
		\begin{oneparchoices}
			\choice Triglyceride
			\choice Phospholipid
			\choice Cholestrol
			\choice Fat
		\end{oneparchoices}
		\question The enzyme lipase is a catalyst for the hydrolysis of \\ 
		\begin{oneparchoices}
			\choice ATP
			\choice Proteins
			\choice Lipids
			\choice Carbohydrates
		\end{oneparchoices}
		\question Which of the following is not a feature common to most animals?
		\begin{choices}
			\choice development into a fixed body plan
			\choice asexual reproduction
			\choice specialized tissues
			\choice heterotrophic nutrient sourcing
		\end{choices}
		\question Crustaceans are \noindent\rule{1in}{0.4pt}. \\
		\begin{oneparchoices}
			\choice ecdysozoans
			\choice nematodes
			\choice arachnids
			\choice parazoans
		\end{oneparchoices}
		\question The circulatory fluid in echinoderms is\noindent\rule{1in}{0.4pt}.
		\begin{oneparchoices}
			\choice blood
			\choice mesohyl
			\choice water
			\choice saline
		\end{oneparchoices}
		\question Which of the following is not a member of the phylum Chordata?
		\begin{oneparchoices}
			\choice Cephalochordata
			\choice Echinodermata
			\choice Urochordata
			\choice Vertebrata
		\end{oneparchoices}
		\question . Which of the following situations will lead to natural selection?
		\begin{choices}
			\choice The seeds of two plants land near each other and one grows larger than the other.
			\choice Two types of fish eat the same kind of food, and one is better able to gather food than the other.
			\choice Male lions compete for the right to mate with females, with only one possible winner.
			\choice all of the above
		\end{choices}
		\question The first forms of life on Earth were thought to be 
		\begin{choices}
			\choice	single-celled plants
			\choice prokaryotes
			\choice insects
			\choice large animals such as dinosaurs
		\end{choices}
		\question Which reproductive combination produces hybrids?
		\begin{choices}
			\choice when individuals of the same species in different geographical areas reproduce
			\choice when any two individuals sharing the same habitat reproduce
			\choice when members of closely related species reproduce
			\choice when offspring of the same parents reproduce
		\end{choices}
		\question What are usually the primary producers in an ocean grazing food web? \\
		\begin{oneparchoices}
			\choice plants
			\choice animals
			\choice fungi
			\choice phytoplankton
		\end{oneparchoices}
	\begin{center}
		\subsection*{Fill in the blank space}
	\end{center}
		\question Active transport uses \noindent\rule{1.5in}{0.4pt} to move substances from an area of \noindent\rule{1.5in}{0.4pt} concentration to \noindent\rule{1.5in}{0.4pt} concentration gradient.
		\question A structure of a nerve cell that allows electrical impulses to transmit quickly is \noindent\rule{1.5in}{0.4pt}.
		\question \noindent\rule{1in}{0.4pt} are blood vessels that serve as sites for the exchange of substances with in the body.
		\question \noindent\rule{1.5in}{0.4pt} is a waste product of anaerobic respiration in humans.
		\question \noindent\rule{1.5in}{0.4pt} are tiny cells in out blood that form clots to prevent bleeding.
		\question Mitochondria most likely evolved from \noindent\rule{1in}{0.4pt}.
		\question The process whereby nitrogen is brought into organic molecules is called \noindent\rule{1in}{0.4pt}.
		\question The weight of living organisms in an ecosystem at a particular point in time is known as \noindent\rule{1in}{0.4pt}.
		\question Protists with the capabilities to absorb nutrients from dead organisms are called \noindent\rule{1in}{0.4pt}.
		
	\begin{center}
		\subsection*{Explain the Following}
	\end{center}
		\question Which chamber of the heart pumps blood to the lungs? \vspace{0.5in}
		\question Write at least three common characteristics of all living things \vspace{1in}
		\question What is a monounsaturated fatty acid? \vspace{1in}
		\question Write at least two differences between viruses and bacteria. \vspace{1in}
		\question Which vessels contain valves to keep blood moving in one direction?\vspace{1in}
		\question Compare prokaryotic and eukaryotic cells. \vspace{1in}
		\question In what condition is a plant cell said to be turgid? \vspace{1in}
		\question Explain about the double circulatory system in humans. \vspace{1in}
		\question What are some of the properties of enzymes? \vspace{1in}
		\question Describe three adaptations that allow for flight in birds.\vspace{1in}
		\question What are the wing of a bird and the arm of a human examples of? \vspace{0.5in}
		\question Galápagos medium ground finches are found on Santa Cruz and San Cristóbal islands, which are separated by about 100 km of ocean. Occasionally, individuals from either island fly to the other island to stay. This can alter the allele frequencies of the population through what mechanism?\vspace{0.5in}
		\question What were the first organisms that oxygenated the atmosphere? \vspace{0.5in}
		\question Why do mosses grow well in the Arctic tundra?\vspace{0.5in}
		\question Two species of fish had recently undergone speciation. The males of each species had a different coloring through which the females could identify and choose a partner from her own species. After some time, pollution made the lake so cloudy that it was hard for females to distinguish colors. What might take place in this situation?\vspace{1in}
		\question What are the factors that limit the length of food chains in ecosystems?\vspace{1in}
		
	\end{questions}		
	
\end{document}